Modelling BCG vaccination in the UK

### 2019-07-04 rmds/06-tb-bcg-improv-outcomes.Rmd
updated chapter referencing

# Exploring the effects of BCG vaccination in patients diagnosed with tuberculosis: observational study using the Enhanced Tuberculosis Surveillance system {#benefical-bcg-out}

>>>>

# Exploring the effects of BCG vaccination in patients diagnosed with tuberculosis: observational study using the Enhanced Tuberculosis Surveillance system {#beneficial-bcg-out}

### 2019-07-04 rmds/index.Rmd
updated chapter referencing

* **Chapter \@ref(benefical-bcg-out):** This chapter uses regression analysis to explore the evidence that BCG vaccination is associated with positive outcomes for active TB cases in England. Any evidence that this is the case may strengthen the case for extending BCG vaccination coverage.

>>>>

* **Chapter \@ref(beneficial-bcg-out):** This chapter uses regression analysis to explore the evidence that BCG vaccination is associated with positive outcomes for active TB cases in England. Any evidence that this is the case may strengthen the case for extending BCG vaccination coverage.
